Title

### 2020-12-01 documents/DraftReport.Rmd
added draft exploratory figure for posterior medians

>>>>

```{r load results, results = 'hide', message = FALSE}

test <- readRDS(here::here('data', 'out1_1.Rdata'))

#for investigating, particularly scenarios where survivals are low
sc <- c(9)
niter <- 25

test <- data.frame()
for (s in sc) {
  for (i in 1:niter) {

temp <- data.frame(readRDS(file = here::here('data', paste0('out', s, '_', i, '.Rdata')))) 
temp.med <- data.frame(t(apply(temp, 2, median)))
temp.med$iter <- i
temp.med$scenario <- s
test <- rbind(test, temp.med)
  }
}

#posterior medians for fec, mean.p, mean.phi[1:2], p.surv, phi.nest
sc <- c(1:5, 11:15)
niter <- 25

meds <- data.frame()
for (s in sc) {
  for (i in 1:niter) {

temp <- data.frame(readRDS(file = here::here('data', paste0('out', s, '_', i, '.Rdata')))) 
temp.med <- data.frame(t(apply(temp, 2, median)))
temp.med$iter <- i
temp.med$scenario <- s

meds <- rbind(meds, temp.med)
  }
}

sc <- c(6:10)
niter <- 25

meds2 <- data.frame()
for (s in sc) {
  for (i in 1:niter) {

temp <- data.frame(readRDS(file = here::here('data', paste0('out', s, '_', i, '.Rdata')))) 
temp.med <- data.frame(t(apply(temp, 2, median)))
temp.med$iter <- i
temp.med$scenario <- s

meds2 <- rbind(meds2, temp.med)
  }
}

meds <- bind_rows(meds, meds2)

post.meds <- meds %>% transform(scenario = factor(scenario)) %>%
  reshape2::melt(id.vars = c('scenario', 'iter')) %>%
    filter(variable %in% c('mean.phi.1.', 'mean.phi.2.', 'mean.p', 'fec', 'p.surv', 'phi.nest'))

true_vals <- data.frame(scenario = rep(1:15, times = 6),
                        variable = rep(c('mean.phi.1.', 'mean.phi.2.', 'mean.p', 'fec', 'p.surv', 'phi.nest'), 
                                       each = 15),
                        value = c(rep(c(0.8, 0.3, 0.8, 0.3, 0.5), times = 3), #adult phi
                                  rep(c(0.7, 0.2, 0.7, 0.2, 0.4), times = 3), #juv phi
                                  c(0.8, 0.8, 0.3, 0.3, 0.5, rep(NA, 5), c(0.8, 0.8, 0.3, 0.3, 0.5)), #mean.p
                                  rep(NA, 15), #fec: what goes here?
                                  rep(c(0.85, 0.85, 0.3, 0.3, 0.5), times = 3), #p.surv
                                  rep(c(0.995, 0.975, 0.995, 0.975, 0.99), times = 3))) #phi.nest

ggplot(post.meds, aes(y = value, x = scenario, group = scenario)) +
  geom_boxplot() +
  geom_point(size = 0.7, col = 'darkgrey') + 
  geom_point(data = true_vals, aes(y = value, x = scenario, group = scenario), col = 'darkred') +
  xlab('Scenario') + ylab('Posterior medians') +
  facet_wrap(~variable, scales = 'free_y') +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 90))
